\chapter*{Acknowledgement}
% First of all, I would like to express my gratitude to Prof~H.~Hamagaki for his apropriate advice and 
% His knowledge and 
% I think I was one of the worst student 
%
% K.~Yako as my supervisor 
% I'm also grateful to Dr~T.~Gunji for his encouragement. 
% I think he for my lazyness. 
% Y.~Watanabe, Y.~L.~Yamaguchi
% great advice
% secretary cns
%
% Y~.Sekiguchi, K.~Terasaki, H.~Murakami
% everyone CNS with the great atmosphere. 

% I also RIKEN supported finantially

% I would like to thank the people in ALICE TRD, in particular Heidelberg group 
% Dr~G.~Simatovic his frendship
% Prof.~K.~Oyama

% I also S.~Yano and D.~Watanabe. 
% S.~Mizuno
% I always remember at Darmstad
% Thank you to everybody of ALICE Japan group.

% chair
% Co-chair

% Finally, I would like to express my all thanks to my parents and sisters, and tomoko.



First of all, I would like to express my gratitude to my supervisor, Prof. H. Hamagaki, for his appropriate advice and profound comments on my analysis and physics. His rich knowledge and entire support guided me to the completion of this thesis.
I am grateful to Dr. T. Gunji for his wealth of knowledge about physics and analysis techniques. 
His strong encouragement enable me to write my thesis successfully.  

I wish to thank Prof. K. Oyama for his great help ans support on TRD work at CERN. 
I would like to express my appreciations to Dr. Y.~L.~Yamaguchi, Dr. Y.~Watanabe, Y.~Hori, R.~Akimoto for their useful advice and kindness. 
Discussions with them have been illuminating. 

Thank you to T. Tsuji, Y.~Sekiguchi, K.~Terasaki, H.~Murakami for their frendship and kindness. 
I'm happy to spent a lot of time with you in my PhD. 

I also thank ALICE TRD group for giving an oppotunity of the great expeariance and great help. 
In particular, the frendship and kindness of Dr. J. Mercado, Dr. G. Simatovic is my treasure. 

I am also deeply grateful to S. Yano, D. Watanabe.
I never forget the wonderful experience and journey at CERN.  

I also thank to all members of ALICE Japan group for their support. 
I also thank Prof. En'yo and RIKEN Rad. Lab Group for their help. 
They also support me finantially and it was also great help of my PhD life.  

I appreciate all the members of the Center for Nuclear Study, University of Tokyo for their generous support and kindness, especially the CNS secretaries, Ms. M. Hirano, Ms. T. Endo, Ms. I. Yamamoto, Ms. Y. Kishi, Mr. Yoshimura, and Mr. Oki.
I really apprecite their great help of the office procedure. 
%Their great help 

%I am obliged to Prof. A. Ejiri, Prof. K. Fukushima, Prof. R. Hayano, Prof. N. Imai, and Prof. H. Miyatakefor their valuable comments and important advice. I would like to appreciate Prof. K. Tokushuku for his truly relevant advice.

%Finally, I would like to thank my parents, and sisters. 
